Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-10 journal/content.tex
Commented out notes

\section{Large scale agile development}

Laanti 2008:
[2] Kähkönen Tuomo, “Agile Methods for large organizations – building communities of practice”.
Proc. Agile Development Conf. (ADC), 2004, pp. 2-10.
[7] Eckstein Jutta, “Agile Software Development in the large: Diving into the deep”,
Dorset House Publishing, 2004. ISBN 0-932633-57-9.
[8] Leffingwell Dean, “Scaling Software Agility: Best Practices for Large Enterprises”,
Addison-Wesley Professional, 2007. ISBN-10: 0321458192.
[12] Highsmith J., Agile for the Enterprise, “From Agile Teams to Agile Organizations”,
Cutter, 2005. http://www.cutter.com/program/ fulltext/reports/2005/01/index.html .
[13] Schwaber Ken, “Enterprise and Scrum”, Microsoft Press 2007, ISBN-10: 0735623376.

Vlaanderen 2012:
22. Sidky, A.S.: A Structured Approach to Adopting Agile Practices: The Agile Adop-
tion Framework (June 2007)

Cockburn 2003:
R. Crocker, Large-Scale Agile Software Development, Addison-Wesley, 2003.

@@

\section{Summary of things that may need to be explained}

* Scrum

* XP

* Definition of sprint

* Definition of product owner

* Self organization and independence of teams -- This is a question relating how
  to organize management.

* Scrum master must not command and control -- Scrum master as manager??

* People centricity -- agile is not for squeezing efficiency -- agile is not for
  fewer career opportunities in a flatter organization.

* Team centricity -- agile focuses on team rather than individuals

* Agile focuses on short time horizons ???

* Agile is a mindset -- it can not be studied from a book -- need of coaching

* What are the agile principles? What is being talked about when ``agile
  principles'' is referred to?

* What is coaching? Why is it done?

* Principle of build often? Principle of nightly builds or CI? Is this from XP?
  Is this an agile principle?

* Kotter: Having a ``guiding team'' for change

>>>>

% \section{Large scale agile development}
% 
% Laanti 2008:
% [2] Kähkönen Tuomo, “Agile Methods for large organizations – building communities of practice”.
% Proc. Agile Development Conf. (ADC), 2004, pp. 2-10.
% [7] Eckstein Jutta, “Agile Software Development in the large: Diving into the deep”,
% Dorset House Publishing, 2004. ISBN 0-932633-57-9.
% [8] Leffingwell Dean, “Scaling Software Agility: Best Practices for Large Enterprises”,
% Addison-Wesley Professional, 2007. ISBN-10: 0321458192.
% [12] Highsmith J., Agile for the Enterprise, “From Agile Teams to Agile Organizations”,
% Cutter, 2005. http://www.cutter.com/program/ fulltext/reports/2005/01/index.html .
% [13] Schwaber Ken, “Enterprise and Scrum”, Microsoft Press 2007, ISBN-10: 0735623376.
% 
% Vlaanderen 2012:
% 22. Sidky, A.S.: A Structured Approach to Adopting Agile Practices: The Agile Adop-
% tion Framework (June 2007)
% 
% Cockburn 2003:
% R. Crocker, Large-Scale Agile Software Development, Addison-Wesley, 2003.

@@

% \section{Summary of things that may need to be explained}
% 
% * Scrum
% 
% * XP
% 
% * Definition of sprint
% 
% * Definition of product owner
% 
% * Self organization and independence of teams -- This is a question relating how
%   to organize management. 
% 
% * Scrum master must not command and control -- Scrum master as manager??
% 
% * People centricity -- agile is not for squeezing efficiency -- agile is not for
%   fewer career opportunities in a flatter organization.
% 
% * Team centricity -- agile focuses on team rather than individuals
% 
% * Agile focuses on short time horizons ???
% 
% * Agile is a mindset -- it can not be studied from a book -- need of coaching
% 
% * What are the agile principles? What is being talked about when ``agile
%   principles'' is referred to?
% 
% * What is coaching? Why is it done?
% 
% * Principle of build often? Principle of nightly builds or CI? Is this from XP?
%   Is this an agile principle?
% 
% * Kotter: Having a ``guiding team'' for change
